Consistency scores in text data

### 2020-08-06 outputs/documents/paper.Rmd
BERT implementation write-up

There are a few packages for implementing a Word2Vec model in R. The packages are "rword2vec" by Mukul Chaware and "word2vec" by Jan Wijffels, BNOSAC, and Max Fomichev. Both packages uses the same algorithm that Word2Vec uses to produce word representations, but they do not have an affiliation with Google. Another way to implement a Word2Vec model in R is through Keras package. Keras is an API for deep learning written in Python (@chollet2015keras) and the Keras package provides an R interface to Keras **(Ke-Li add citation for the package)**. RStudio published a tutorial for implementing the skip-gram model of Word2Vec (@falbel2017word) through Keras. We intend to follow this tutorial as the approach to implement a Word2Vec model. There are three basic steps within the Keras deep learning framework: first is to prepare the data, second is to define the model and third is to train and evaluate the model. Following the steps, we first downloaded a the Amazon Fine Foods Reviews dataset from Stanford **(Ke-Li add citation for data set)** and preprocess the text into tokens. Then we defined a model that mimics the skip-gram algorithm of Word2Vec. The embedding dimensions, the size of the context window and the number of samples are configurable. Finally, we used the fit_generator() function of Keras to train the model. **What's supposed to happen:** As a result, a embedding matrix is obtained and serves as the look-up table of the word vectors. **What really happened:** However, the training process was stuck in the operation of fit_generator() function.

@@

There are more than one way to implement GloVe word embedding model in R. One way is to load GloVe embeddings into a frozen Keras Embedding layer **(Keli add citation to the blog post by Keras)** using the Keras R package **(Keli add citation to package)**. Another way, as mentioned and briefly demonstrated by Rstudio in their blog post, is to use the "text2vec" package developed by Dmitriy Selivanov **(Ke-Li add package citation)**. Keras published a blog post on pre-trained word embeddings through GloVe in R. In this project, we intend to follow the blog post for implementing GloVe through the Keras R package **(Keli add citation to the blog post by Keras)**. The blog post is aimed to create a word embedding model for text classification. However, we will only use the guide create a embedding matrix and skip the steps of text classification. Since we are employing Keras again, the process remains similar. We first retrieved the training data set from Stanford and preprocessed the text in to tokens. We then defined the model by configuring the embedding layer. Finally the model is trained and evaluated, and the GloVe embedding matrix is obtained.

@@

BERT implementation in R is also possible through Keras. Zhao HG (**Replace by citation**) created a python module called "keras-bert" and the module can be called by R through "reticulate" package (@reticulateR), which enables the operation of Python modules in R. To start, the "keras-bert" module is installed in Python environment and is called in R through the 'reticulate' package. We can then load, configure and train the BERT model. To train the BERT model, we load a task-specific dataset for it to learn. [(**Keli Add more details**)]

>>>>

There are a few packages for implementing a Word2Vec model in R. The packages are "rword2vec" by Mukul Chaware and "word2vec" by Jan Wijffels, BNOSAC, and Max Fomichev. Both packages uses the same algorithm that Word2Vec uses to produce word representations, but they do not have an affiliation with Google. Another way to implement a Word2Vec model in R is through Keras package. Keras is an API for deep learning written in Python (@chollet2015keras) and the Keras package provides an R interface to Keras **(Ke-Li add citation for the package)**. RStudio published a tutorial for implementing the skip-gram model of Word2Vec (@falbel2017word) through Keras. We intend to follow this tutorial as the approach to implement a Word2Vec model. There are three basic steps within the Keras deep learning framework: first is to prepare the data, second is to define the model and third is to train and evaluate the model. Following the steps, we first downloaded a the [Amazon Fine Foods Reviews dataset from Stanford] **(Ke-Li add citation for data set)** and preprocess the text into tokens. Then we defined a model that mimics the skip-gram algorithm of Word2Vec in a function called skipgrams_generator(). The embedding dimensions, the size of the context window and the number of samples are configurable within this function. Finally, we used the fit_generator() function of Keras to train the model. **What's supposed to happen:** As a result, a embedding matrix is obtained and serves as the look-up table of the word vectors. **What really happened:** However, the training process was stuck in the operation of fit_generator() function. According to Stack Flow this might be an issue of incompatible versions between Keras and Tensorflow. More investigation is needed.

@@

There are more than one way to implement GloVe word embedding model in R. One way is to load GloVe embeddings into a frozen Keras Embedding layer **(Keli add citation to the blog post by Keras)** using the Keras R package **(Keli add citation to package)**. Another way, as mentioned and briefly demonstrated by Rstudio in their blog post, is to use the "text2vec" package developed by Dmitriy Selivanov **(Ke-Li add package citation)**. Keras published a blog post on pre-trained word embeddings through GloVe in R. In this project, we intend to follow the blog post for implementing GloVe through the Keras R package **(Keli add citation to the blog post by Keras)**. The blog post is aimed to create a word embedding model for text classification. However, we will only use the guide create a embedding index and skip the steps of text classification. Instead of building a model for word embedding from scratch as we did for the skip-gram model of Word2Vec, here we are merely loading the Glove model and its pretrained word vectors as an index. The word embedding index is then saved to an R environment.

@@

BERT implementation in R is also possible through Keras. Zhao HG (**Replace by citation**) created a python module called "keras-bert" and the module can be called by R through "reticulate" package (@reticulateR), which enables the operation of Python modules in R. To start, we install the keras-bert model in Python on the machine and load BERT model into R through "reticulate". Once keras-bert is loaded, we can use it to fine-tune BERT on a task-specific training dataset. Fine-tuning is started by tokenizing the training data. The output of the tokenization is then fed to BERT as the input. The next step is to define the model by configuring its parameters such as batch size, number of epochs and the learning rate. Finally, the model is compiled and we can begin the fine-tuning.
